We need to beat namespotting, no idea how

### 2023-01-16 paperSubmission/paperSubmission1.tex
small changes

 In line with this discussion, for the purpose of our study we have distinguished two types of counter responses to personal attacks: ``empathetic'' and ``normative''. The empathetic approach is aimed at countering the so-called desensitization to violence. It is a very dangerous process, finally leading to dehumanization of stigmatized groups. %Unfortunately, the impersonal structure of online space makes it very easy for the desensitization to occur. 
 Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice. By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.

The normative approach stems from the  aforementioned psychological research of normative social influence, stating that in ambiguous situations, people tend to rely on social cues, to determine what kinds of behaviors will be accepted. Taking from these studies, we refer to two types of norms: injunctive norms---describing what the members of this community are supposed to do and what is approved or disapproved by others (laws, rules, code of conduct, savoir-vivre, etc.) and descriptive norms - what the members of this community actually do \citep{cialdini_focus_1991, cialdini2004social, cialdini2006managing}.

@@

>>>>

 In line with this discussion, for the purpose of our study we have distinguished two types of counter responses to personal attacks: ``empathetic'' and ``normative''. The empathetic approach is aimed at countering the so-called desensitization to violence. It is a very dangerous process, finally leading to dehumanization of stigmatized groups. %Unfortunately, the impersonal structure of online space makes it very easy for the desensitization to occur. 
 Being frequently exposed to online hate speech builds tolerance to the phenomenon and as a result we no longer see such statements as offensive, which lowers our sympathy for the victims and increases prejudice. By sending empathetic interventions we hoped to evoke compassion, self-reflection and humanize the person on the other side of the screen \citep{bilewicz2021artificial}.  The normative approach

@@

\todo{To sie nie klei ta koncowka, trzeba cos zmienic}
